\documentclass[line, margin]{res3address}
\usepackage{enumitem}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}

\begin{document}

\name{Adam S. Jermyn}
\address{Home: 18 Duxbury Lane, Longmeadow, MA 01106-2006, USA}
\address{University: Churchill College, Storey's Way, Cambridge CB3 0DS, Tel 011-44-(0)-749-0397012, UK}
\address{Online: adamjermyn@gmail.com, adamjermyn.com, github.com/adamjermyn}

\begin{resume}

\section{Education}
PhD, Astronomy, University of Cambridge, Churchill College, Institute of Astronomy\hfill 2015-18\\
\phantom{4ex} Dissertation: Turbulence and Transport in Stars and Planets (doi:10.17863/CAM.25347)\\
\phantom{4ex} Funded by UK Marshall Scholarship\\
\phantom{4ex} Supervisors: Christopher Tout and Gordon Ogilvie\\
BS, Physics, California Institute of Technology\hfill 2011-15\\
\phantom{4ex} Academic Advisors: Tom Tombrello and Jason Alicea\\
\phantom{4ex} Senior Thesis: The Atmospheric Dynamics of Pulsar Companions (Sterl Phinney)\\
\phantom{4ex} GPA: 4.2/4.3, Class Rank: 2/239, In-Major GPA: 4.3/4.3, In-Major Rank: 1/31

\section{Research}
Flatiron Research Fellow, Center for Computational Astrophysics\hfill 2019-21\\
KITP Postdoctoral Scholar, UCSB\hfill 2018-19

\section{Awards}
Institute of Astronomy Paul Murdin Prize (for best paper by a PhD student)\hfill 2017\\
\vspace{-1em}
\begin{quote}
Awarded for the best paper by a PhD student at the Institute of Astronomy. ``Jermyn’s paper develops a new mechanism for the problem of swollen, hot Jupiter planets. The paper is particularly noteworthy for its development of analytic theory combining radiative insolation, tidal heating, and vibrational modes.''
\end{quote}
\vspace{-1em}
APS LeRoy Apker Award\hfill 2015\\
\vspace{-1em}
\begin{quote}
For original contributions to understanding how the atmospheres of pulsar companions are heated and for elucidating the observational consequences.
\end{quote}
\vspace{-1em}
Caltech George W. Housner Award for Original Research\hfill 2015\\
\vspace{-1em}
\begin{quote}
Awarded to a senior selected for an outstanding piece of original scientific research.
\end{quote}
\vspace{-1em}
Caltech Frederic W. Hinrichs, Jr. Memorial Leadership Award\hfill 2015\\
\vspace{-1em}
\begin{quote}
Awarded to the seniors who, in the opinion of the undergraduate deans, have made the greatest undergraduate contribution to the welfare of the student body and whose qualities of leadership, character, and responsibility have been outstanding.	
\end{quote}
\vspace{-1em}
Caltech Dr. D. S. Kothari Prize\hfill 2015\\
\vspace{-1em}
\begin{quote}
Awarded to a graduating senior in physics who has produced an outstanding research project during the year.
\end{quote}
\vspace{-1em}
Caltech Library Senior Thesis Prize\hfill 2015\\
\vspace{-1em}
\begin{quote}
For the thesis titled “The Atmospheric Dynamics of Pulsar Companions.”, described by the prize committee as a “tour de force in its breadth of scholarship, creativity and significance”.\\	
\end{quote}
\vspace{-1em}
\vspace{-1em}
Caltech Haren Lee Fisher Memorial Award in Physics\hfill 2014\\
\vspace{-1em}
\begin{quote}
Awarded to a junior physics major who demonstrates the greatest promise of future contributions in physics.
\end{quote}
\vspace{-1em}
Caltech Jack E. Froehlich Memorial Award\hfill 2014\\
\vspace{-1em}
\begin{quote}
Awarded to a junior in the upper 5 percent of his or her class who shows outstanding promise for a creative professional career.
\end{quote}
\vspace{-1em}
Caltech Perpall Scientific Speaking Competition 2nd Place\hfill 2014\\
\vspace{-1em}
\begin{quote}
Awarded after a three-round competition of presentations following a Summer Undergraduate Research Fellowship.	
\end{quote}
\vspace{-1em}
US Physics Team (top 20 in US on semifinal exam), Member\hfill 2011\\
First Place Massachusetts State Science Fair\hfill 2010\\
\vspace{-1em}
\begin{quote}
Awarded for a project analyzing plasma flow computationally.
\end{quote}
\vspace{-1em}

\section{Grants}
Hertz Fellowship\hfill 2015\\
NSF Graduate Fellowship\hfill 2015\\
NDSEG Graduate Fellowship (declined)\hfill 2015\\
Marshall Scholarship\hfill 2014\\
\phantom{4ex} Renewed 2017-18\hfill 2017\\
Barry M. Goldwater Fellowship\hfill 2014\\
Flintridge Foundation Summer Undergraduate Research Fellowship\hfill 2014\\
US Department of Energy NERSC Allocation m1824 (PI):\\
\phantom{4ex} Renewal Allocation (PI, 50,000 core-hours) \hfill 2017\\
\phantom{4ex} Renewal Allocation (PI, 50,000 core-hours) \hfill 2016\\
\phantom{4ex} Renewal Allocation (PI, 50,000 core-hours) \hfill 2015\\
\phantom{4ex} Renewal Allocation (PI, 15,000 core-hours) \hfill 2014\\
\phantom{4ex} Startup Allocation (15,000 core-hours) \hfill 2013\\
Jean J. Dixon Summer Undergraduate Research Fellowship\hfill 2013\\
Ph11 Summer Research Fellowship\hfill 2012\\


\section{Professional Memberships}
Royal Astronomical Society\hfill 2016-17\\
Association of Marshall Scholars\hfill 2015-17\\
American Physical Society\hfill 2013-17\\
Materials Research Society\hfill 2012-2015

\section{Papers}
\textbf{Published:}
\begin{enumerate}[leftmargin=10pt]
\item \textbf{Jermyn, A. S.}, Steinhardt, C. L., Tout, C. A. The Cosmic Microwave Background and the Stellar Initial Mass Function. Monthly Notices of the Royal Astronomical Society (2018).
\item Tagliabue, G, \textbf{Jermyn, A. S.}, Sundararaman, R, Welch, A. J., DuChene, J. S., Davoyan, A. R., Narang, P, Atwater, H. Hot Carrier Dynamics in Photoexcited Gold Nanostructures: Role of Interband Excitations and Evidence for Ballistic Transport. arXiv:1708.02187. Nature Communications (2018).
\item \textbf{Jermyn, A. S.}, Tout, C. A., Chitre, S. M. Enhanced Mixing in Massive Rotating Stars. arXiv:1807.08766. Monthly Notices of the Royal Astronomical Society (2018).
\item Rasmussen, A*, \textbf{Jermyn, A. S.*} Gapless Topological Order, Gravity, and Black Holes. Physical Review B (2018, PhysRevB97.165141, arXiv:1703.04772).
\item \textbf{Jermyn, A. S.}, Kama, M. Stellar Photospheric Abundances as a Probe of Disks and Planets. Monthly Notices of the Royal Astronomical Society (2018, 476 (4): 4418-4434, arXiv:1804.06414).
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M. Turbulence Closure for Mixing Length Theories. Monthly Notices of the Royal Astronomical Society (2018 476 (1): 646-662, arXiv:1803.00579). \textbf{Invited listing in the newsletter of the IAU Working Group on Red Giants and Supergiants.}
\item Steinhardt, L., C., \textbf{Jermyn, A. S.} Nonparametric Methods in Astronomy: Think, Regress, Observe -- Pick Any Three. Proceedings of the Astronomical Society of the Pacific (2017, 130, 984, arXiv:1801.06545).
\item Halabi, G. M., Izzard, R. G., Tout, C. A., \textbf{Jermyn, A. S.}, Cannon, R. 2DStars: A two-dimensional stellar evolution code. Mem. S.A.It. (2017 Vol. 75, 282).
\item \textbf{Jermyn, A. S.}, Tout, A. C., Ogilvie, I. G. Tidal heating and solar irradiation of Hot Jupiters. Monthly Notices of the Royal Astronomical Society (2017 469 (2): 1768-1782, arXiv:1704.01126).
\item Cortés, E, Xie, W, Cambiasso, J, \textbf{Jermyn, A. S.}, Sundararaman, R, Narang, P, Schl\"{u}cker, S, Maier, S. Hot Electron Transport Driven Surface-Chemistry with Nanoscale Spatial Resolution. Nature Communications (2017).
\item Narang, P*, Sundararaman, R*, \textbf{Jermyn, A. S.}, Atwater, H, Goddard, W. Cubic nonlinearity driven upconversion in high-field plasmonic hot carrier systems. The Journal of Physical Chemistry C (2016).
\item Chatwin-Davies, A, \textbf{Jermyn, A. S.}, Carroll, S. Retrieving Qubits from Black Holes. Physical Review Letters (2015, Phys.Rev.Lett.115,261302, arXiv:1507.03592). \textbf{Highlighted in Science News}.
\item Sundararaman, R*, Narang, P*, \textbf{Jermyn, A. S.*}, Atwater, H, Goddard, W. Theoretical predictions for hot carrier generation from surface plasmon decay. Nature Communications 5, 5788 (2014).
\item\textbf{Jermyn, A. S.}, Mong, R, Alicea, J. Stability of zero-modes in parafermion chains. Physical Review B (2014, PhysRevB.90.165106, arXiv:1407.6376). \textbf{Editor's Suggestion (front webpage)}.
\end{enumerate}

\textbf{Submitted: (preprints upon request unless specified)}
\begin{enumerate}[leftmargin=10pt]
\item \textbf{Jermyn, A. S.}, Loeb, A. Transit Seismology. 2018.
\item \textbf{Jermyn, A. S.}, Cao, W., Elam, W. A., De La Cruz, E. M., Lin, M. M. Equilibrium self-assembly of one-dimensional protein structures. 2018.
\item \textbf{Jermyn, A. S.} Efficient Decomposition of High-Rank Tensors. arXiv:1708.07471. 2017.
\item \textbf{Jermyn, A. S.}, Tagliabue, G, Atwater, H, Goddard, W, Sundararaman, R, Narang, P. Far-from-equilibrium transport of excited carriers in nanostructures. arXiv:1707.07060.
\item \textbf{Jermyn, A. S.}, Stevenson, D. J. Levitin, D. J. From Bach to Shamu: $1/f$ laws in non-human music. 2016.
\end{enumerate}

\textbf{Preprint:}
\begin{enumerate}[leftmargin=10pt]
\item \textbf{Jermyn, A. S.} Automatic Contraction of Unstructured Tensor Networks. arXiv:1709.03080. 2017.
\item \textbf{Jermyn, A. S.} Bounding the Radius of Convergence of Analytic Functions. arXiv:1708.00343. 2017.
\end{enumerate}

\section{Talks}
\textbf{Invited:}
\begin{enumerate}[leftmargin=10pt]
\item \textbf{Jermyn, A. S.}, Kama, M (2018), Probing the composition of disks and planets through accretion onto radiative stars. Cambridge Stars Group Talk.
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M.  (2017), Enhanced Rotational Mixing in Massive Stars. Caltech Tea Talk.
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M.  (2017), Enhanced Rotational Mixing in Massive Stars. UCSB Lunch Talk.
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M.  (2017), Enhanced Rotational Mixing in Massive Stars. Princeton Lunch Talk.
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M.  (2017), Enhanced Rotational Mixing in Massive Stars. Harvard CfA Group Meeting.
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M.  (2017), Enhanced Rotational Mixing in Massive Stars. MIT Astro Brown Bag Lunch Talk.
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M.  (2017), Mixer: Numerical Perturbation Theory for Turbulence. Harvard ITC Lunch Seminar.
\item \textbf{Jermyn, A. S.}, Narang, P., Sundararaman, R.  (2017), Charge Transport: Ballistics and Diffusion. Kavli Discussion, Harvard SEAS.
\item \textbf{Jermyn, A. S.}, Tout, C. A., Chitre, S. M., Lesaffre, P. (2017), Meridional Flow and Mixing in Massive Stars. Cake Talk, Neils Bohr Institute, University of Copenhagen.
\item \textbf{Jermyn, A. S.}, Tout, C. A., Chitre, S. M., Lesaffre, P. (2017), Meridional Flow and Mixing in Massive Stars. Seminar, Institute of Astronomy, University of Cambridge.
\item \textbf{Jermyn, A. S.}, Phinney, E.S. (2016). The Atmospheric Dynamics of Pulsar Companions. Invited Talk (Apker Prize), APS April.
\item \textbf{Jermyn, A. S.}, Mong, R, Alicea, J (2014), Stability of zero-modes in parafermion chains. Institute for Quantum Information and Matter.
\end{enumerate}
\textbf{Contributed:}
\begin{enumerate}[leftmargin=10pt]
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C. A., Chitre, S. M.  (2018), Enhanced Rotational Mixing in Massive Stars. UK National Astronomical Meeting.
\item \textbf{Jermyn, A. S.} (2018). Efficient Contraction of Unstructured Tensor Networks. APS March.
\item \textbf{Jermyn, A. S.}, Tout, C. A., Chitre, S. M., Lesaffre, P. (2017), Meridional Flow and Mixing in Massive Stars. Bridge Chemical Evolution Meeting (2017).
\item \textbf{Jermyn, A. S.}, Tout, C. A., Chitre, S. M., Lesaffre, P. Tidal Heating and Solar Irradiation of Hot Jupiters. Churchill Conference on Everything (2017).
\item \textbf{Jermyn, A. S.} (2017). Automatic Renormalization of Local Tensor Networks. APS March.
\item \textbf{Jermyn, A. S.}, Phinney, E.S. (2015). Exterior Stellar Heating. APS Apker Finalist Seminar.
\item \textbf{Jermyn, A. S.}, Sundararaman, R, Narang, P, Goddard, W, Atwater, H (2015). Plasmonic Hot Carrier Transport and Collection in Nanostructures. APS March.
\item \textbf{Jermyn, A. S.}, Phinney, E.S. (2014). Exterior Stellar Heating. Caltech SURF Seminar.
\item \textbf{Jermyn, A. S.}, Mong, R, Alicea, J (2014), Robustness of zero-modes in parafermion chains. APS March.
\item \textbf{Jermyn, A. S.}, Alicea, J, Mong, R (2013), The Stability of Zero Energy Edge Modes in 1D Quantum Chains. Caltech SURF Seminar.
\item \textbf{Jermyn, A. S.} (2010). The Fluid Behavior of Electron Aggregates. Massachusetts Junior Academy of Sciences Symposium.
\end{enumerate}

\section{POSTERS}
\begin{enumerate}[leftmargin=10pt]
\item \textbf{Jermyn, A. S.}, Lesaffre, P, Tout, C, A 2D Magnetic Mixing Length Theory. Cambridge Fluids Network Meeting 2016.
\item Sundararaman, R, Narang, P, \textbf{Jermyn, A. S.}, Brown, A, Goddward, W, Atwater, H, Generation and transport of hot carriers in plasmonic nanostructures. Joint Center for Artificial Photosynthesis All-Hands 2015.
\item Narang, P, Sundararaman, R, \textbf{Jermyn, A. S.}, Bouma, L, Goddard, W, Atwater, H, Surface Plasmon Decay Dynamics: A Feynman Diagram Approach. Gordon Research Conference 2014.
\item Sundararaman, R, Narang, P, \textbf{Jermyn, A. S.}, Atwater, H, Goddard, W, First principles theory of plasmonic hot carrier generation in nano-structured systems. Gordon Research Conference 2014.
\item Narang, P, Sundararaman, R, \textbf{Jermyn, A. S.}, Localized Surface Plasmon Decay Dynamics. MRS Spring 2014.
\item Sundararaman, R, Narang, P, \textbf{Jermyn, A. S.}, Atwater, H, Goddard, W, First Principles Calculations for Surface Plasmon Decays and Solvation Models for Surfaces in Solution. Joint Center for Artificial Photosynthesis All-Hands 2014.
\item Narang, P, Sundararaman, R, \textbf{Jermyn, A. S.}, Creel, E, Atwater, H, Goddard, W, Plasmon-driven Solar Energy Conversion and Catalysis: A First Principles Study. Joint Center for Artificial Photosynthesis All-Hands 2014.
\item Markovic, N, Silverman, S, \textbf{Jermyn, A. S.}, Rivera, R. Optical Properties of Unfunctionalized Ultra-Short Carbon Nanotubes. Poster 135, MRSEC Summer Research Experience Poster Session 2010. 
\end{enumerate}

\section{Patents}
\textbf{Jermyn, A. S.}, Silverman, J, Markovic, N, ''System for Lightweight Image Processing," US Patent Number US 9,097,739 B2 (Filed 2011, Awarded 2015).

\section{Software}
AstroStatsSuite - Statistical tools for non-parametric regression in astronomy (GPLv3, github)\hfill 2017-\\
PyTNR - Python module for automatically contracting unstructured tensor networks (GPLv3, github)\hfill 2017-\\
TensorDecomp - Python module for computing tree decompositions of tensors (GPLv3, github)\hfill 2017-\\
arrfunc - Python module for treating functions as lazily-evaluated arrays (MIT, github)\hfill 2017-\\
2D Stars - Cambridge 2D Stellar Evolution Code. Cofounding Developer\hfill 2015-\\
QuantumScattr - Quantum carrier transport code. Cofounding Developer\hfill 2012-17\\
AstroMicroPhysics - Python astronomical microphysics package. Lead Developer.\hfill 2015\\
QuantumChains - Numerical Condensed Matter Package (GPLv3, github). Lead Developer. \hfill 2013-14\\
NanoImage - Atomic Force Microscopy Analysis (USPTO 13/534428). Lead Developer. \hfill 2010-11\\

\section{Teaching}
\textbf{Cambridge Supervisor:}\\
\phantom{4ex} Mathematics: Numerical Analysis (Part IB)\hfill 2018\\
\phantom{4ex} Mathematics: Mathematical Biology (Part II)\hfill 2017\\
\phantom{4ex} Mathematics: Binary Stars (Part III - Masters Course)\hfill 2017\\
\phantom{4ex} Mathematics: Computational Projects (Part IB)\hfill 2016\\
\phantom{4ex} Mathematics: Structure and Evolution of Stars (Part III - Masters Course)\hfill 2016\\
\phantom{4ex} Natural Sciences: Mathematics (Part IA)\hfill 2016\\
\phantom{4ex} Physics: Astrophysical Fluid Dynamics (Part II)\hfill 2015\\
\textbf{Caltech Teaching Assistant:}\\
\phantom{4ex} Ph101 - Order of Magnitude Physics (Prof. E. S. Phinney) \hfill 2015\\
\phantom{4ex} Ph11 - Freshman Research Tutorial (Profs. David Stevenson and Rob Phillips)\hfill 2014-15\\
\phantom{4ex} Ph7 - Radiation Lab (Graduate TA/Section Leader for Dr. Frank Rice) \hfill 2014\\
\phantom{4ex} Ph6 - Atomic Physics Lab (Graduate TA/Section Leader for Dr. Frank Rice) \hfill 2014\\
\phantom{4ex} Ph5 - Analog Circuits Lab (Undergraduate TA for Dr. Frank Rice) \hfill 2013\\
\phantom{4ex} Ph6 - Atomic Physics Lab (Undergraduate TA for Dr. Frank Rice) \hfill 2013\\
\textbf{Caltech Tutor:}\\
\phantom{4ex} Ph205a - Relativistic Quantum Field Theory\hfill 2014-15\\
\phantom{4ex} Ph106 - Graduate Classical Mechanics and Electromagnetism\hfill 2013-15\\
\phantom{4ex} Ph127 - Graduate Statistical Physics\hfill 2013-15\\
\phantom{4ex} Ph236a - General Relativity\hfill 2013-15\\
\phantom{4ex} Ch1 - Freshmen Chemistry\hfill 2012-15\\
\phantom{4ex} Ma1 - Freshmen Math (Analysis, Linear Algebra, Multivariable Calculus)\hfill 2012-15\\
\phantom{4ex} Ma2 - Sophomore Math (Probability, Statistics, and Differential Equations)\hfill 2012-15\\
\phantom{4ex} Ph2 - Sophomore Physics (Waves, Quantum Mechanics, and Thermodynamics)\hfill 2012-15\\
\phantom{4ex} Ph12 - Advanced Sophomore Physics (Waves, Quantum Mechanics, and Thermodynamics)\hfill 2012-15\\
\phantom{4ex} ACM95 - Graduate Methods of Applied and Computational Mathematics\hfill 2012-15\\
\phantom{4ex} Ph125 - Graduate Quantum Mechanics\hfill 2012-15\\
\textbf{Caltech Guest Lecturer:}\\
\phantom{4ex} Ph50 - Physics League (Seminar)\hfill 2017\\
\phantom{4ex} Ph11 - Freshman Research Tutorial\hfill 2013, 2016, 2017\\
\textbf{Unaffiliated Tutor:}\\
\phantom{4ex} High School Physics Olympiad Preparation\hfill 2016\\
\textbf{Other:}\\
\phantom{4ex} Experimental Design (Thin Film Deposition) for Senior Lab\hfill 2014\\
\phantom{4ex} Editor, Ph5 Laboratory Manual\hfill 2013

\section{Outreach}
\begin{enumerate}[leftmargin=10pt]
\item Contributed text on the history of stellar dynamics to an upcoming biography of James Jeans. 2017.
\item Volunteer at Cambridge Science Festival. 2016-17.
\item \textbf{Jermyn, A. S.}, Tout, C. A., Chitre, S. M., Lesaffre, P. Mixing in Massive Stars. Churchill MCR ChuTalk (Outreach Talk) (2017).
\item Co-Organized Institute of Astronomy Undergraduate Journal Club. 2016-17.
\item \textbf{Jermyn, A. } Gravitational waves open new window to cosmos. Reach for the Stars Guest Column on MassLive. URL: \url{http://www.masslive.com/living/index.ssf/2016/03/reach_for_the_stars_gravitational_waves_open_new_window_to_cosmos.html}. March 2016.
\item Volunteer at Cambridge Institute of Astronomy Public Outreach events 2016.
\item Handmer, C. \textbf{Jermyn, A. S.}, Paragano, M., Lommen, P, Nosanov, J. The Martian: A Technical Commentary. URL: \url{http://caseyexaustralia.blogspot.co.uk/2015/10/the-martian-technical-commentary.html}. October 2015.
\item \textbf{Jermyn, A. S.}, Hung, P. Caltech Teaching Conference Opening Session. Caltech Center for Teaching, Learning, and Outreach Invited Talk. September 2014.
\item \textbf{Jermyn, A. S.} A Summer of Physics. Invited talk at the Skyscrapers Amateur Astronomical Society of Rhode Island. July 2011.
\item Guest speaker at the Springfield Telescope and Reflector Society and Amherst Area Amateur Astronomy Association. 6 times in 2006-2012.
\end{enumerate}

\section{Employment}
Undergraduate IT Support\hfill 2011-14

\section{Skills}
\textbf{Programming Languages:}\\
\phantom{4ex} Experienced: Python (NumPy/SciPy), Java, Mathematica, C++, Julia, Matlab\\
\phantom{4ex} Familiar: C, Fortran, Bash\\
\phantom{4ex} Passable: R, Scheme\\
\textbf{Other:}\\
\phantom{4ex} Programming and using Finite Element codes\\
\phantom{4ex} Density Matrix Renormalization Group methods\\
\phantom{4ex} Markov Chain and Nested Sampling methods\\
\phantom{4ex} Massively parallel programming\\
\phantom{4ex} Finite Difference Time Domain EM Simulations (Meep)\\
\phantom{4ex} Familiarity with Unix/Linux environments

\section{Service}
\textbf{Cambridge:} \\
\noindent
Representative to the Institute of Astronomy Athena SWAN/Juno committee\hfill 2016-17\\
Institute of Astronomy Computing Users' Committee\hfill 2017\\
Astronomy Graduate Student Forum Representative\hfill 2015-17\\
Representative to the School of Physical Sciences Graduate Education Committee Workshop\hfill 2016\\
\textbf{Caltech:} \\
\noindent
Search Committee for the Vice President for Student Affairs\hfill 2014-15\\
Dean's Advisory Council \hfill 2014-15\\
Contributing Writer - The California Tech\hfill 2014-15\\
Academics and Research Committee\hfill 2012-15\\
Curriculum Committee\hfill 2012-15\\
Commencement Speaker Selection Committee\hfill 2014-15\\
Physics Student Faculty Conference Committee \hfill 2013-15\\
Physics Option Mentor \hfill 2013-15\\
Upperclassmen Counselor\hfill 2013-15\\
Council for Undergraduate Education\hfill 2013-15\\
Information Management Systems and Services Representative\hfill 2012-15\\
Title IX Committee\hfill 2014-15\\
Faculty Board Ad Hoc Honor Code Task Force\hfill 2013-14\\
Undergraduate Honor Code Committee\hfill 2013-14\\
Housing Stewardship Committee\hfill 2013-14\\
Dabney House Treasurer\hfill 2013-14\\
Computer Advisory Committee\hfill 2012-14\\
Dabney House Comptroller\hfill 2012-13\\
\end{resume}

\end{document}
